---
title: "HW 1"
author: "Eric Xue"
date: "9/18/2021"
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(knitr, tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

**Write this homework acting as if I don't know what I asked you. For example, don't simply list question numbers for the headings. If you gave this document to someone else who didn't know the assignment, they should be able to understand what you did by reading the headings, code, and accompanying text.**

**Look to my HW1 and RMarkdown Organization examples for how to write good headings and organize your assignment.**

This HW is worth 10 total points.

This assignment is pretty straightforward but offers a lot of room for creativity. I look forward to seeing what you'll create!

1. Change the author and date fields in the header above to your name and the date.

2. Make sure to load any packages you may need right at the start. Do *NOT* include the `learnr` package, ever, unless you are writing an interactive Tutorial (which you won't do in this) - this will cause problems.

3. Ensure that no chunks have the `include = FALSE` or `echo = FALSE` option, as I want to be able to see *all* your code and output.

4. Brief but descriptive headings and document organization (answers under headings, text near relevant code, brief explanatory text as indicated below, etc.) (1 pt)

5. **Create a map.** It must have at least two groups/regions. Those groups/regions should be colored according to some value of a third valuable. In other words, make a map that displays some interesting differences across a geographic area. 

    You can choose any geographic area you want and can find map data for in R. Examples might include U.S. states; different countries in Europe, Asia, Africa, or the Americas; and Chinese provinces. (Because I suspect many of you might be interested in mapping within China: For some reason, at least for me, using `map_data("china")` and the `ggplot()` methods we discussed produces an incorrect map with odd, piecemeal provincial borders. I do not know why. If you have the same problem, as a solution I recommend using [Guangchang Yu's `chinamap` package](https://github.com/GuangchuangYu/chinamap). You install it using `remotes::install_github("GuangchuangYu/chinamap")`, then create the map data frame using the `get_map_china()` function. From there you should be able to use the techniques we learned to generate a provincial map. [Here](https://guangchuangyu.github.io/chinamap/) are some examples of maps he made with that package. Note he uses a slightly different technique, `geom_map()`, but `geom_polygon()` seems to work just fine, too. Let me know if you're having difficulty here, though!)

    The variable you map can be *anything* that varies across the geographic area you're mapping. It cannot be from a data frame included in Tutorial 7.1, but otherwise you are free to choose whatever interests you! Note this part of the assignment does require you to find some data on your own (though it can be a data frame we've worked with in the past), import it, and link it to the map data. Linking may be a bit tricky - remember the region names will have to match *exactly*, including in capitalization. Use functions like `str_to_lower()` to help with that. 

    **Describe** in narrative text what your code is doing. I want more detail than usual - you can describe the importing and linking briefly (about 1 sentence or comment per code block), but for the map-related code itself I want you to describe it essentially line by line. Basically, prove to me you can explain, in your own words, what your code is doing and how it's working to create the map. (4.5 pts)
    
6. **Create an interactive plot using `plot_ly().**

    You may either update a former static plot you made (for example, in your QTM 150 Final Project) to be interactive, or create an entirely new interactive plot. You may not simply alter any plot used in any prior Tutorial. 

    You should give the plot a brief but descriptive title, and informative axis titles. You don't explicitly know how to do this yet, but part of the challenge is to research it on your own (via Google or other means) and find out! It's not too difficult, I promise. 
    
    **Describe** in narrative text what your code is doing. Once again I want more detail than usual - you can describe any preparatory code briefly (about 1 sentence or comment per code block), but for the plotly code itself I want you to describe it essentially line by line. Basically, prove to me you can explain, in your own words, what your code is doing and how it's working to create the interactive plot. (4.5 pts)
    
**To submit this assignment:**

Ideally, knit straight to PDF by changing `html_document` to `pdf_document` in line 5 above. This should work as long as you properly installed LaTeX in Tutorial 0.1. Otherwise:

1. Knit to HTML. An HTML document should open automatically in another RStudio window.

2. Click "Open in Browser" in that HTML document. It should open as a webpage in your default browser (e.g. Chrome).

3. Click Ctrl+P/Command+P, but instead of printing a hard copy on your printer click "Save as PDF."

4. Save and upload that document to Canvas.
    
    


------BEGIN ANSWER BELOW--------

# China Population and other Countries's Population Growth

#### *The Data*
```{r}
# Load chinamap and plotly packages

pacman::p_load(chinamap,plotly,tidyverse)
china_province<-read.csv("china_provinces_population.csv")
pop_by_country <- read.csv("population-by-country.csv")
china_map <- get_map_china()
head(china_map)
```
We first load the package of chinamap and plotly, which contain the map of china and the tools we need to build a interactive plot. Then, we read the data of china population by province and population by countries into R for later use.

#### *Static Map of China by Province *
```{r}
china_combine <- china_map %>% 
    left_join(china_province, by = c("province" = "PROVINCE.NAME"))
# Combine the datasets of china population by province and china map. So China map now has a column for the population of each province
ggplot(china_combine, aes(x = long, y = lat, fill = POPULATION))+
# Use the dataset china_combine with x-axis being longitude, y-axis being latitude, and different color represents the population difference. 
    geom_polygon(aes(group=group), color = "black") + 
# Use polygon to draw the map with black lines.
    scale_fill_viridis_c(option = "B", direction = 1) +
# Change to the color set I like and with the direction that darker color represents more population
    labs(title = "China Population by Province", x = "Longitutde", y = "Latitude") + 
# Add titles and change the name of x-axis and y-axis
    coord_fixed(1.3)
# Keep the map without being stretched
```
This graph shows the population in each province of China. The darker the color is, more people live in there. In most of provinces, there is a positive relationship between the size of the province and the number of people live in there. However, the province where the major cities are located does not have this association. Even though the province is small, it still has many people

**Explantion of the code:**

First we prepare the dataset by linking china_province and china map with the name of province being the key. Then I create a map in ggplot by using geom_polygon. x and y are longitude and latitude and color of the province represents the population of the province. Geom_polygon draws the map according to the group in the dataset. Finally, I add titles, change the name of x-axis and y-axis, and fix the aspect ratio of the map to make it easy to read non-strechable when zoom in and out.

#### *The Growth of Four Countries Population (Interactive Plot)*
```{r}
countries_select <- pop_by_country %>% 
    filter(Entity == c("China", "United States", "United Kingdom", "Switzerland") )
countries_select
plot_ly(data = countries_select,
        x = ~ Year,
        y = ~ Population.by.Country..Clio.Infra..2016..,
        color = ~Entity,
        colors = "Dark2") %>% 
    add_trace(type = "scatter",
              mode = "lines+markers") %>% 
    layout(title = "Population Growth of Four Countries", xaxis = list(title = "Year"), yaxis=list(title = "Population"))
```

China has the biggest population base and the fastest population growth than the other three countreis. United states has the second fastest population growth. 


Prepare the dataset by keeping the population data of only four countries. Using the dataset of countries_select and plotly to create an interactive plot with x being year, y being the population of that year, and different colors of the line to represent different countries. Colors= specifies the color theme used. I use add_trace so I can have multiple parameters for my line. In this case, I have the line with the dot on it. Finally, I adjust the layout to set title and the name of x-axis and y-axis. For the x-axis and y-axis, I need to use list() because there are multiple attributes to the axises.